A generalized definition of multidimensional item response theory parameters

### 2022-11-11 output/paper_draft/paper_M2PLM_parameters.Rmd
Adds Proposition 2 and proof

**Proposition 1.** Under the previously defined conditions, for all
$`r TRAIT_VEC_IN_LS`$,

@@

\begin{equation}
  `r DIAG_MATRIX_INNER_PROD_EQ`.
\end{equation}

@@

>>>>

**Proposition 1** Under the previously defined conditions, for all
$`r TRAIT_VEC_IN_LS`$,

@@

\begin{equation}
  `r DIAG_MATRIX_INNER_PROD_EQ`.
\end{equation}
<!-- # TODO: I have changed here $D^{-1/2}$ by $D$; discuss with Mario -->

@@

We can also obtain a result that relates the direction cosines of any two bases.

::: {#prp-dir-cosines-bases-relationship}

**Proposition 2** Let's consider another basis $`r ALT_BASIS_EQ`$ in
$`r LATENT_SPACE`$ and the inner product $`r ALT_BASIS_INNER_PROD`$ that keeps
the norm of the Euclidean space invariant.

Let $`r DIR_COS_VEC_ALT`$ be the vector of direction cosines of
$`r TRAIT_VECTOR`$ in $`r ALT_BASIS`$ (i.e., the cosines with the elements of
$`r ALT_BASIS`$).

Then,

\begin{equation}
  `r DIR_COS_VEC_ALT_EQ`,                      (\#eq:dir-cosines-transformation)
\end{equation}

where

\begin{equation}
  `r DIAG_MATRIX_INNER_PROD_ALT_EQ`
\end{equation}

and $`r TRANSFORM_MATRIX_ALT_EQ`$.
<!-- TODO: Comment with Mario (order of terms inverted here) -->

Let's call $`r TRAIT_COORDS_ALT_EQ`$ and let $`r TRANSFORM_MATRIX_ALT_EQ`$
be the change of basis matrix, such that $`r TRAIT_TRANSFORM_ALT_EQ`$.

Then, we have that $`r BASIS_CHANGE_ORG_ALT_EQ`$.

The inner product $`r ALT_BASIS_INNER_PROD`$ that keeps the norm invariant is
defined by $`r INNER_PROD_TRAIT_ALT_EQ`$, and we define
$`r INNER_PROD_MATRIX_ALT_EQ`$.

By proposition 1, for each case we have:

1. $`r TRAIT_VEC_STD_POLAR_EQ`$

1. $`r TRAIT_VECTOR_POLAR_EQ`$

1. $`r TRAIT_VEC_ALT_POLAR_EQ`$

Given (1),

\begin{equation}
  `r TRAIT_VEC_STD_POLAR_EQ_XPAND`
\end{equation}

and

\begin{equation}
  `r TRAIT_VEC_ALT_POLAR_ALT_EQ`.
\end{equation}

Using (2) and (3) we get that

\begin{equation}
  `r TRAIT_VEC_STD_POLAR_ORG_EQ`
\end{equation}

and

\begin{equation}
  `r TRAIT_VEC_STD_POLAR_ALT_EQ`.
\end{equation}

\begin{equation}
  `r TRAIT_VEC_POLAR_ORG_ALT_COEFF_EQ`,
\end{equation}

and thus $`r DIR_COS_VEC_ALT_EQ`$.$`r END_OF_PROOF`$
